Augraphy: A Data Augmentation Library for Document Images

### 2023-02-11 paper.tex
space
Updates from Overleaf
Spelling correction

\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce the level of complexity in the document lifecycle at seen in the real world.  Such real-world conditions and  features have direct implementations either within the library or on the development roadmap.

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/shabbyreal_denoised.png}
\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
\label{fig:shabbyreal_denoised}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/shabbypages_denoising.png}
\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
\label{fig:shabbypages_denoising}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{figures/ocr_figure.png}
\caption{Sample \emph{ShabbyReal} clean/noisy image pair, and the OCR output for each. The computed Levenshtein distance between the OCR result strings is 203.}
\label{fig:ocr_output}
\end{figure}

>>>>

\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce the level of complexity in the document lifecycle as seen in the real world.  Such real-world conditions and  features have direct implementations either within the library or on the development roadmap.

@@

\begin{figure}
\centering
\includegraphics[width=0.9\columnwidth]{figures/shabbyreal_denoised.png}
\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
\label{fig:shabbyreal_denoised}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\columnwidth]{figures/shabbypages_denoising.png}
\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
\label{fig:shabbypages_denoising}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\columnwidth, frame]{figures/ocr_figure.png}
\caption{Sample \emph{ShabbyReal} clean/noisy image pair, and the OCR output for each. The computed Levenshtein distance between the OCR result strings is 203.}
\label{fig:ocr_output}
\end{figure}
